Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-04-03 Draft.tex
Updates to draft and reviewer's comments.

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage{natbib}
% \usepackage{color}
% \usepackage[dvipsnames]{xcolor}
\usepackage[margin=1cm]{caption}
%\usepackage{tabularx, booktabs}
%\usepackage{float}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}
\usepackage{lineno}

@@

% \newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
% \newcommand{\jarad}[1]{{\color{Orange} JARAD: #1}}

@@

\newcommand{\pdet}{p^{(det)}}
\newcommand{\ind}{\stackrel{ind}{\sim}}
\newcommand{\Fm}{F_T^{(M)}}

@@

Our analysis is motivated by avian point-count surveys in Chippewa National Forest from 2008-2013 as part of the Minnesota Forest Breeding Bird Project (MNFB) \citep{Hanowski1995}.  
%However, the model we describe is appropriate for point-count surveys of any species, so long as time-to-first-detection data are available.  
For our analysis, we focus on Ovenbird counts selected from one habitat type: sawtimber red pine stands with no recent logging activity.  
Each stand had up to four sites with sufficient geographical distance between sites to reduce or eliminate overlapping territories.
The data included 65 sites and a total of 381 surveys with site specific variables including site age,  stock density, and an indicator of select-/partial-cut logging during the 1990s. 
A total of 947 Ovenbirds were counted with a maximum of eight in any single survey.  
% The counts of Ovenbirds by interval, across all sites, were 596, 69, 62, 68, 43, 33, 35, 27, and 14.

@@

Before considering interval censoring and explanatory variables, we first present the scenario of exact time to detections with no explanatory variables. 
We then incorporate interval censoring and follow with inclusion of fixed and random effects for abundance and detection.

@@

A common choice for TTDD is an exponential distribution, i.e. $T_{sb}\ind \mbox{Exp}(\varphi)$, which imposes a constant first detection rate, i.e. $h(t) = \varphi$.
Choosing another TTDD can allow for a systematic non-constant detection regime. 
For example, to model an observer effect where: (i) the observer's arrival suppresses or stimulates detectable cues, but (ii) organisms acclimate and gradually return to constant detection, a gamma TTDD could be appropriate.
%In addition to an exponential and gamma TTDD, we also consider Weibull and lognormal as these distributions are often used in survival analysis. 
Like the gamma TTDD, Weibull and lognormal TTDDs offer the flexibility of a two-parameter form and allow rates to either increase or decrease during the survey; however, the shapes of these distributions differ, most notably in tail probability.
All three could be reasonable TTDD choices if, for instance, detection rates vary among individuals.
This leads to marginal detection rates that decrease over time as individuals with higher detection rates are removed from the population.

@@

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
The first study compares mixture vs non-mixture models.
The second study compares the TTDD families.
In the first two studies, we utilized intercept only models to focus attention on robustness of the TTDD choice in the most simple of scenarios.
For the third study, we included fixed and random effects for both abundance and detection and again compared the distribution families. 
Because our main goal with these studies was to demonstrate poor performance under model misspecification, and because the computation time for sampling from some models was large, we simulated only a small number of replicates.
In all simulation studies, we focused on accuracy in estimation of $\pdet$ which then translated into estimation of abundance.

In the following analyses we distinguish two categories of purely continuous TTDDs: peaked and nonpeaked.  
Detection rates $h(t)$ of peaked distributions generally decrease over time, while detection rates of nonpeaked distributions generally increase over time.
More formally, we define a peaked TTDD as having a mode greater than zero (or $C_1$ for lognormal) while a non-peaked TTDD has a mode of zero (or less than $C_1$), but we consider exponential TTDDs to be neither peaked nor nonpeaked.

@@

\ifdic
\begin{table}[ht]\centering\small
\begin{tabular}{l|l|l|l|cccc|cccc||r}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c||}{\underline{Mixture model}} & \\
 \multicolumn{4}{c|}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & Med. $p$ & Q($p$) & 50\% & 90\% & $\Delta$ DIC \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.76 & 0.41 & 0.75 & 0.88 & 0.84 & 0.66 & 0.56 & 0.94 & 0.24 \\ 
 & & &   Lognormal & 0.66 & 0.17 & 0.31 & 0.62 & 0.78 & 0.48 & 0.62 & 1.00 & -0.67 \\ 
 & & &   Weibull & 0.69 & 0.25 & 0.38 & 0.75 & 0.79 & 0.51 & 0.75 & 1.00 & 0.37 \\ 
  \cline{3-13}
 & & &   Exponential & 0.80 & 0.54 & 0.44 & 0.94 & 0.79 & 0.38 & 0.31 & 0.88 & 1.48 \\ 
  \cline{3-13}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} &  Gamma & 0.80 & 0.55 & 0.50 & 1.00 & 0.82 & 0.70 & 0.38 & 0.88 & 0.96 \\ 
 & & &   Lognormal & 0.78 & 0.31 & 0.50 & 0.94 & 0.80 & 0.48 & 0.62 & 1.00 & 0.97 \\ 
 & & &   Weibull & 0.79 & 0.49 & 0.56 & 0.94 & 0.82 & 0.66 & 0.44 & 0.88 & 1.28 \\ 
  \cline{2-13}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.17 & 0.12 & 0.81 & 0.76 & 0.41 & 0.69 & 1.00 & 0.51 \\ 
 & & &   Lognormal & 0.56 & 0.04 & 0.00 & 0.31 & 0.72 & 0.30 & 0.44 & 0.88 & 0.33 \\ 
 & & &   Weibull & 0.51 & 0.02 & 0.00 & 0.06 & 0.71 & 0.32 & 0.44 & 1.00 & 2.40 \\ 
  \cline{3-13}
 & & &   Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.77 & 0.37 & 0.38 & 0.94 & 122.81 \\ 
  \cline{3-13}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.74 & 0.33 & 0.31 & 0.88 & 31.84 \\ 
 & & &   Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.76 & 0.36 & 0.38 & 0.94 & 63.65 \\ 
 & & &   Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.70 & 0.29 & 0.56 & 0.94 & 28.30 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$ (true value = 0.80).  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 16 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.  
$\Delta$ DIC: mean difference in DIC between the incorrect-mixture model minus the true model.
}
\label{tbl:sim1}
\end{table}

\else

\begin{table}[ht]\centering\small
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & Med. $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.76 & 0.41 & 0.75 & 0.88 & 0.84 & 0.66 & 0.56 & 0.94 \\ 
 & & &   Lognormal & 0.66 & 0.17 & 0.31 & 0.62 & 0.78 & 0.48 & 0.62 & 1.00  \\ 
 & & &   Weibull & 0.69 & 0.25 & 0.38 & 0.75 & 0.79 & 0.51 & 0.75 & 1.00 \\ 
  \cline{3-12}
 & & &   Exponential & 0.80 & 0.54 & 0.44 & 0.94 & 0.79 & 0.38 & 0.31 & 0.88  \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} &  Gamma & 0.80 & 0.55 & 0.50 & 1.00 & 0.82 & 0.70 & 0.38 & 0.88 \\ 
 & & &   Lognormal & 0.78 & 0.31 & 0.50 & 0.94 & 0.80 & 0.48 & 0.62 & 1.00 \\ 
 & & &   Weibull & 0.79 & 0.49 & 0.56 & 0.94 & 0.82 & 0.66 & 0.44 & 0.88 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.17 & 0.12 & 0.81 & 0.76 & 0.41 & 0.69 & 1.00 \\ 
 & & &   Lognormal & 0.56 & 0.04 & 0.00 & 0.31 & 0.72 & 0.30 & 0.44 & 0.88 \\ 
 & & &   Weibull & 0.51 & 0.02 & 0.00 & 0.06 & 0.71 & 0.32 & 0.44 & 1.00 \\ 
  \cline{3-12}
 & & &   Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.77 & 0.37 & 0.38 & 0.94 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.74 & 0.33 & 0.31 & 0.88 \\ 
 & & &   Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.76 & 0.36 & 0.38 & 0.94 \\ 
 & & &   Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.70 & 0.29 & 0.56 & 0.94 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$ (true value = 0.80).  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 16 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.  
}
\label{tbl:sim1}
\end{table}
\fi

@@

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Oral Prelim/Posteriors_Families_draft"}
\caption{\label{fig:sim2typical} 
Representative example of the posterior distributions for $\pdet$ from exponential (light solid line) and gamma (dark solid line) mixture models fit to data simulated from nonpeaked gamma (shape$<$1), exponential (shape$=$1), and peaked gamma (shape$>$1) mixture TTDDs, with true detection probabilities shown for comparison (dashed vertical line, $\pdet=0.8$). 
}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage{natbib}
\usepackage{color}
% \usepackage[dvipsnames]{xcolor}
\usepackage[margin=1cm]{caption}
%\usepackage{tabularx, booktabs}
%\usepackage{float}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}
\usepackage{lineno}

@@

\newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
% \newcommand{\jarad}[1]{{\color{Orange} JARAD: #1}}

@@

\newcommand{\pdet}{p^{(det)}}
\newcommand{\ind}{\stackrel{ind}{\sim}}
\newcommand{\Fm}{F_T^{(M)}}
\newcommand{\nobs}{n^{(obs)}}

@@

Our analysis is motivated by avian point-count surveys in Chippewa National Forest from 2008-2013 as part of the Minnesota Forest Breeding Bird Project (MNFB) \citep{Hanowski1995}.  
%However, the model we describe is appropriate for point-count surveys of any species, so long as time-to-first-detection data are available.  
For our analysis, we focus on Ovenbird counts selected from one habitat type: sawtimber red pine stands with no recent logging activity.  
Each stand had up to four sites with sufficient geographical distance between sites to reduce or eliminate overlapping territories.
This dataset includes 947 Ovenbirds counted in 381 surveys at 65 sites with site-specific variables including site age,  stock density, and an indicator of select-/partial-cut logging during the 1990s.
% The counts of Ovenbirds by interval, across all sites, were 596, 69, 62, 68, 43, 33, 35, 27, and 14.

@@

\adam{I think we start by describing our joint likelihood: p(counts $| N, \pdet$) and p(times $|$ counts,TTDD) and prior.
We explain that, in isolation, $N$ and $\pdet$ are not identifiable in the first piece, which is why we use the second piece to inform our estimates of $\pdet$.
Then, in the body of section \ref{sec:exact_time}, we introduce a second paragraph which defines our distribution for $\nobs$ and completes the data likelihood.
The discussion of identifiability would travel with the distribution of $\nobs$ and be cleaned up a little.
Perhaps even split the discussion of TTDDs into another subsection.
}

Before considering interval censoring and explanatory variables, we first present the scenario of exact times to detections with no explanatory variables. 
We then incorporate interval censoring and follow with inclusion of fixed and random effects for abundance and detection.

@@

A common choice for TTDD is an exponential distribution, i.e. $T_{sb}\ind \mbox{Exp}(\varphi)$, which imposes a constant first detection rate, i.e. $h(t) = \varphi$.
Choosing another TTDD can allow for a systematic non-constant detection regime. 
For example, to model an observer effect where: (i) the observer's arrival suppresses or stimulates detectable cues, but (ii) organisms acclimate and gradually return to constant detection, a gamma TTDD could be appropriate.
%In addition to an exponential and gamma TTDD, we also consider Weibull and lognormal as these distributions are often used in survival analysis. 
Like the gamma TTDD, Weibull and lognormal TTDDs offer the flexibility of a two-parameter form and allow rates to either increase or decrease during the survey; however, the shapes of these distributions differ, most notably in tail probability.
All three may be reasonable TTDD choices if, for instance, detection rates vary among individuals.
This leads to marginal detection rates that decrease over time as individuals with higher detection rates are removed from the population.

@@

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
The first study compares mixture vs non-mixture models.
The second study compares the TTDD families.
In the first two studies, we utilized intercept only models to focus attention on robustness of the TTDD choice in the most simple of scenarios.
For the third study, we included fixed and random effects for both abundance and detection and again compared the distribution families. 
In all simulation studies, we focused on accuracy in estimation of $\pdet$ which then translated into estimation of abundance.

In the following analyses we distinguish two categories of purely continuous TTDDs: peaked and nonpeaked.  
Detection rates $h(t)$ of peaked distributions generally increase over time, while detection rates of nonpeaked distributions generally decrease over time.
More formally, we define a peaked TTDD as having a mode greater than zero (or $C_1$ for lognormal) while a non-peaked TTDD has a mode of zero (or less than $C_1$), but we consider exponential TTDDs to be neither peaked nor nonpeaked.

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/mixture_fig"}
\caption{
Comparisons of data and models with and without mixture TTDDs.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 50\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}: Data simulated from non-mixture (upper) or mixture (lower) TTDDs.  \textit{Columns}:  Data simulated from nonpeaked (left), exponential (center), or peaked (right) TTDDs.  In these simulations, each inference model was only fit to datasets from the same TTDD family (e.g. lognormal to lognormal).
}
\label{fig:mixture_fig} 
\end{figure}

% FIRST SUBMISSION TABLE
%\ifdic
%\begin{table}[ht]\centering\small
%\begin{tabular}{l|l|l|l|cccc|cccc||r}
% \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c||}{\underline{Mixture model}} & \\
% \multicolumn{4}{c|}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & Med. $p$ & Q($p$) & 50\% & 90\% & $\Delta$ DIC \\ 
%  \hline
%  \hline
% \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.76 & 0.41 & 0.75 & 0.88 & 0.84 & 0.66 & 0.56 & 0.94 & 0.24 \\ 
% & & &   Lognormal & 0.66 & 0.17 & 0.31 & 0.62 & 0.78 & 0.48 & 0.62 & 1.00 & -0.67 \\ 
% & & &   Weibull & 0.69 & 0.25 & 0.38 & 0.75 & 0.79 & 0.51 & 0.75 & 1.00 & 0.37 \\ 
%  \cline{3-13}
% & & &   Exponential & 0.80 & 0.54 & 0.44 & 0.94 & 0.79 & 0.38 & 0.31 & 0.88 & 1.48 \\ 
%  \cline{3-13}
% & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} &  Gamma & 0.80 & 0.55 & 0.50 & 1.00 & 0.82 & 0.70 & 0.38 & 0.88 & 0.96 \\ 
% & & &   Lognormal & 0.78 & 0.31 & 0.50 & 0.94 & 0.80 & 0.48 & 0.62 & 1.00 & 0.97 \\ 
% & & &   Weibull & 0.79 & 0.49 & 0.56 & 0.94 & 0.82 & 0.66 & 0.44 & 0.88 & 1.28 \\ 
%  \cline{2-13}
%& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.17 & 0.12 & 0.81 & 0.76 & 0.41 & 0.69 & 1.00 & 0.51 \\ 
% & & &   Lognormal & 0.56 & 0.04 & 0.00 & 0.31 & 0.72 & 0.30 & 0.44 & 0.88 & 0.33 \\ 
% & & &   Weibull & 0.51 & 0.02 & 0.00 & 0.06 & 0.71 & 0.32 & 0.44 & 1.00 & 2.40 \\ 
%  \cline{3-13}
% & & &   Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.77 & 0.37 & 0.38 & 0.94 & 122.81 \\ 
%  \cline{3-13}
% & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.74 & 0.33 & 0.31 & 0.88 & 31.84 \\ 
% & & &   Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.76 & 0.36 & 0.38 & 0.94 & 63.65 \\ 
% & & &   Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.70 & 0.29 & 0.56 & 0.94 & 28.30 \\ 
%   \hline
%\end{tabular}
%\caption{Summary of mixture vs. non-mixture model fits.  
%In all cases, the inference model family matches the dataset family.  
%Med $p$: average across simulations of the posterior median of $\pdet$ (true value = 0.80).  
%Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
%50\% and 90\% coverage is expressed as the proportion of 16 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.  
%$\Delta$ DIC: mean difference in DIC between the incorrect-mixture model minus the true model.
%}
%\label{tbl:sim1}
%\end{table}
%
%\else
%
%\begin{table}[ht]\centering\small
%\begin{tabular}{l|l|l|l|cccc|cccc}
% \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
% \multicolumn{4}{c|}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & Med. $p$ & Q($p$) & 50\% & 90\% \\ 
%  \hline
%  \hline
% \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.76 & 0.41 & 0.75 & 0.88 & 0.84 & 0.66 & 0.56 & 0.94 \\ 
% & & &   Lognormal & 0.66 & 0.17 & 0.31 & 0.62 & 0.78 & 0.48 & 0.62 & 1.00  \\ 
% & & &   Weibull & 0.69 & 0.25 & 0.38 & 0.75 & 0.79 & 0.51 & 0.75 & 1.00 \\ 
%  \cline{3-12}
% & & &   Exponential & 0.80 & 0.54 & 0.44 & 0.94 & 0.79 & 0.38 & 0.31 & 0.88  \\ 
%  \cline{3-12}
% & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} &  Gamma & 0.80 & 0.55 & 0.50 & 1.00 & 0.82 & 0.70 & 0.38 & 0.88 \\ 
% & & &   Lognormal & 0.78 & 0.31 & 0.50 & 0.94 & 0.80 & 0.48 & 0.62 & 1.00 \\ 
% & & &   Weibull & 0.79 & 0.49 & 0.56 & 0.94 & 0.82 & 0.66 & 0.44 & 0.88 \\ 
%  \cline{2-12}
%& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.17 & 0.12 & 0.81 & 0.76 & 0.41 & 0.69 & 1.00 \\ 
% & & &   Lognormal & 0.56 & 0.04 & 0.00 & 0.31 & 0.72 & 0.30 & 0.44 & 0.88 \\ 
% & & &   Weibull & 0.51 & 0.02 & 0.00 & 0.06 & 0.71 & 0.32 & 0.44 & 1.00 \\ 
%  \cline{3-12}
% & & &   Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.77 & 0.37 & 0.38 & 0.94 \\ 
%  \cline{3-12}
% & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.74 & 0.33 & 0.31 & 0.88 \\ 
% & & &   Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.76 & 0.36 & 0.38 & 0.94 \\ 
% & & &   Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.70 & 0.29 & 0.56 & 0.94 \\ 
%   \hline
%\end{tabular}
%\caption{Summary of mixture vs. non-mixture model fits.  
%In all cases, the inference model family matches the dataset family.  
%Med $p$: average across simulations of the posterior median of $\pdet$ (true value = 0.80).  
%Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
%50\% and 90\% coverage is expressed as the proportion of 16 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.  
%}
%\label{tbl:sim1}
%\end{table}
%\fi

% THIS IS SIMILAR TO THE ABOVE TABLE FOR ALL FOUR PDET SIMULATIONS.
% WE DEEMED IT TO OPPRESSIVE AND INSTEAD GENERATED THE FIGURES CURRENTLY IN THE PLOT
%\begin{table}[ht]\centering\footnotesize
%\setlength{\tabcolsep}{4pt} %default is 6
%\begin{tabular}{l|l|l|l|cccc|cccc||cccc|cccc}
% \multicolumn{4}{c|}{ } & \multicolumn{8}{c}{\underline{Non-mixture model}} & \multicolumn{8}{c}{\underline{Mixture model}} \\
% \multicolumn{4}{c|}{ } & \multicolumn{4}{c}{\underline{Posterior median}} & \multicolumn{4}{c}{\underline{Coverage}} & \multicolumn{4}{c}{\underline{Posterior median}} & \multicolumn{4}{c}{\underline{Coverage}}\\
% \multicolumn{4}{c|}{ } & p50 & p65 & p80 & p95 & p50 & p65 & p80 & p95 & p50 & p65 & p80 & p95 & p50 & p65 & p80 & p95 \\
%  \hline
%  \hline
%\parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.69 & 0.75 & 0.95 & 0.11 & 0.78 & 0.45 & 0.59 & 0.76 & 0.78 & 0.83 & 0.96 & 0.00 & 0.35 & 0.55 & 0.61 \\ 
%   &  &  & Lognormal & 0.54 & 0.59 & 0.71 & 0.94 & 0.81 & 0.45 & 0.29 & 0.47 & 0.68 & 0.73 & 0.82 & 0.96 & 0.05 & 0.63 & 0.63 & 0.44 \\ 
%   &  &  & Weibull & 0.55 & 0.60 & 0.72 & 0.94 & 0.79 & 0.59 & 0.41 & 0.43 & 0.69 & 0.73 & 0.82 & 0.96 & 0.16 & 0.59 & 0.59 & 0.52 \\ 
%\cline{3-20}
%   &  &  & Exponential & 0.49 & 0.64 & 0.80 & 0.95 & 0.51 & 0.50 & 0.54 & 0.48 & 0.45 & 0.61 & 0.78 & 0.94 & 0.47 & 0.33 & 0.48 & 0.42 \\ 
%\cline{3-20}
%   & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.48 & 0.64 & 0.79 & 0.95 & 0.57 & 0.46 & 0.45 & 0.44 & 0.57 & 0.68 & 0.81 & 0.95 & 0.42 & 0.51 & 0.45 & 0.40 \\ 
%   &  &  & Lognormal & 0.49 & 0.64 & 0.80 & 0.95 & 0.53 & 0.36 & 0.52 & 0.44 & 0.54 & 0.67 & 0.81 & 0.95 & 0.37 & 0.44 & 0.53 & 0.44 \\ 
%   &  &  & Weibull & 0.48 & 0.61 & 0.78 & 0.95 & 0.40 & 0.46 & 0.38 & 0.49 & 0.59 & 0.69 & 0.81 & 0.96 & 0.37 & 0.46 & 0.49 & 0.42 \\ 
%\cline{2-20}
%\cline{2-20}
%& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.62 & 0.60 & 0.64 & 0.85 & 0.42 & 0.78 & 0.11 & 0.03 & 0.71 & 0.71 & 0.75 & 0.91 & 0.10 & 0.81 & 0.64 & 0.31 \\ 
%   &  &  & Lognormal & 0.50 & 0.52 & 0.58 & 0.85 & 0.95 & 0.12 & 0.04 & 0.03 & 0.64 & 0.67 & 0.74 & 0.92 & 0.09 & 0.93 & 0.51 & 0.38 \\ 
%   &  &  & Weibull & 0.50 & 0.51 & 0.54 & 0.71 & 0.92 & 0.23 & 0.01 & 0.01 & 0.64 & 0.66 & 0.70 & 0.87 & 0.39 & 0.92 & 0.46 & 0.28 \\ 
%\cline{3-20}
%   &  &  & Exponential & 0.88 & 0.93 & 0.96 & 0.99 & 0.00 & 0.00 & 0.00 & 0.00 & 0.50 & 0.63 & 0.78 & 0.94 & 0.54 & 0.45 & 0.42 & 0.51 \\ 
%\cline{3-20}
% & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.24 & 0.26 & 0.28 & 0.37 & 0.00 & 0.00 & 0.00 & 0.00 & 0.52 & 0.58 & 0.72 & 0.94 & 0.76 & 0.51 & 0.40 & 0.41 \\ 
%   &  &  & Lognormal & 0.18 & 0.20 & 0.22 & 0.27 & 0.00 & 0.00 & 0.00 & 0.00 & 0.49 & 0.61 & 0.78 & 0.94 & 0.66 & 0.58 & 0.46 & 0.43 \\ 
%   &  &  & Weibull & 0.18 & 0.19 & 0.22 & 0.28 & 0.00 & 0.00 & 0.00 & 0.00 & 0.52 & 0.56 & 0.69 & 0.93 & 0.80 & 0.44 & 0.33 & 0.47 \\ 
%  \hline
%\end{tabular}
%\caption{Summary of mixture vs. non-mixture model fits over 100 replicates.
%In all cases, the inference model family matches the dataset family.  
%Column titles denote the true detection probability (e.g. `p80' means $\pdet = 0.80$). 
%Medians are averaged across all replicates.
%Coverage is for 50\% credible intervals.
%For nominal coverage, we expect values between (0.41, 0.59) 95\% of the time.}
%\label{tbl:sim1}
%\end{table}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/family_fig"}
\caption{
Comparisons of TTDDs across families.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 50\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}: Denote the TTDD family used to simulated data.  \textit{Columns}:  Data simulated from nonpeaked (left) or exponential/peaked (right) TTDDs.  In these simulations, we used only mixture datasets and inference models.
}
\label{fig:family_fig}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/Posteriors_Families_draft"}
\caption{\label{fig:sim2typical} 
Representative examples of posterior distributions for $\pdet$ (left panel) and survey-level log-scale abundance (right panel).
Data are simulated from nonpeaked gamma (left column), exponential (center), and peaked gamma (right) mixture TTDDs.
True detection probabilities are shown for comparison (dashed vertical line) and vary by row.
Inference models are either exponential mixture (light gray) or gamma mixture (dark gray) TTDDs.
}
\end{figure}

% FIRST SUBMISSION TABLE
%\ifdic
%\begin{table}[ht]
%\footnotesize\centering
%\begin{tabular}{l|l|l|ccccc|ccccc}
% \multicolumn{3}{c}{ } & \multicolumn{5}{c}{\underline{Exponential mixture model}} & \multicolumn{5}{c}{\underline{Gamma mixture model}} \\
% \multicolumn{3}{c}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & $\Delta$ DIC & Med. $p$ & Q($p$) & 50\% & 90\% & $\Delta$ DIC \\ 
%  \hline
%\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Data Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.88 & 0.91 & 0.06 & 0.69 & 1.54 & 0.76 & 0.41 & 0.69 & 1.00 & --- \\ 
%& &   Lognormal & 0.92 & 0.99 & 0.00 & 0.12 & 2.08 & 0.85 & 0.72 & 0.44 & 0.69 & 0.93 \\ 
%& &   Weibull & 0.87 & 0.83 & 0.31 & 0.38 & 0.67 & 0.79 & 0.49 & 0.69 & 1.00 & -0.08 \\ 
%\cline{2-13}
%& &   Exponential & 0.77 & 0.37 & 0.38 & 0.94 & --- & 0.68 & 0.24 & 0.25 & 0.81 & -0.97 \\ 
%\cline{2-13}
%& \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.36 & 0.00 & 0.00 & 0.00 & 6.63 & 0.74 & 0.33 & 0.31 & 0.88 & --- \\ 
%& &   Lognormal & 0.34 & 0.00 & 0.00 & 0.00 & 18.54 & 0.84 & 0.73 & 0.44 & 0.81 & 0.71 \\ 
